To implement such software as stated in the requirements section, the Hawk framework will be extended. Hawk is a framework that provides an abstraction about protocol-independent traffic analysis. It also features a currently very limited visualization of the results. There are also modules, which provide extra toolings, like a release integration, or a CI feature.
Although the method of the Hawk framework is novel, one of its biggest limitations is traffic analysis at its core. So the solution is to extend Hawk to support different inputs besides traffic analysis. Possible new inputs could be data loss prevention, code analysis, or different policy languages. Also, a better API is needed, to enable the above-mentioned requirements.\\

As described in the context, there are many privacy-enhancing technologies available to implement. Since the scope to implement all mentioned technology categories would be too big, this implementation will only focus on one. Data loss prevention offers the most promising features, in relation to its comparably simple implementation, as later described in the respective section. This thesis focuses on expanding Hawk, as mentioned above, and adding data loss prevention as an input besides traffic analysis. Since data loss prevention is a really lax defined category of technologies, we only consider DLP implementations, that support data identification with personal data. For this reason, the DLP input abstraction focuses on data identification and risk analysis. The new Hawk Core will also implement the cluster detection module, as defined in functional requirement 2. This module will be based on a cluster/environment detection mechanism, to know which services exist and to resolve certain name references, present in the input abstraction schema. This is cluster-aware, to fulfill the non-functional requirement 3. The module information, together with the results of the present inputs, is then exposed in a REST API, according to functional requirement 3. To present the capabilities of Hawk, a simple report generation tool as an output will be implemented. Ideally, this should generate a preset for a data protection impact assessment. Also, documents of policy languages can be generated. A TILT-based document output might be possible here \cite{grunewald_tilt_2020}.\\